LAs_clusters

### 2020-08-18 src/LAs_Clusters.Rmd
now with a download regression too

## Auxiliary Regression

```{r regressions, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

## Auxiliary Regression without upload variables

```{r regressions no upload and test, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

>>>>

## Auxiliary regression, dep. var.: upload clusters

```{r upload regression, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

## Auxiliary regression, dep. var.: upload clusters, without upload variables

```{r upload regression no upload and test, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

## Auxiliary regression, dep. var.: download clusters

```{r download regression, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

aux <- multinom(cluster.down ~ LAD.down.am20 + LAD.down.pm20 + LAD.tests.pm20 + #  LAD.down.am20 + LAD.down.pm20
                   pop + pop16_64 + # how about young population share
                   managers + tech + skilled +
                   earnings + total.busi, data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.down ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

stargazer(aux, type = "html",
          add.lines = list(c("McFadden's R squared",                    # use rownames as line name. in this case Weak insterumetns
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3), round(r2[1],3), round(r2[1],3),
                              round(r2[1],3))))
